\textsf{Are frontier models superhuman chemists?}

### 2024-03-14 src/tex/ms.tex
clean up workflow
update analysis

In this spider chart, the worst score for every dimension is 0 (no question answered completely correctly) and the best score is 1 (all questions answered correctly). 
Thus, a larger colored area indicates a better performance. 
One can observe that this performance varies widely across models and topics. 
While computational chemistry and biochemistry receive relatively high scores for many models, this is not the cases for topics such as chemical safety or analytical chemistry.
In the subfield of analytical chemistry the prediction of the number of peaks observable in a \gls{nmr} spectrum proved difficult for the models. 
While this question is relatively easy () for trained humans given a drawing of the compounds, models that are only shown the \gls{smiles} string of a compound have to use this to reason about the symmetry of the compound. 
This is mirrored in the questions about point groups of compounds ...

For all topics in chembench, proprietary models outperform their open counterparts.

% Can we say something how this links to changes we have to make to the training data

@@

\section*{Data and code availability}
The code and data for chembench is available at \url{https://github.com/lamalab-org/chem-bench} and archived at \url{XXX}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}. 
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{showyourwork!} framework.\cite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{https://github.com/lamalab-org/chembench-paper}.

>>>>

In this spider chart, the worst score for every dimension is 0 (no question answered completely correctly) and the best score is 1 (all questions answered correctly). 
Thus, a larger colored area indicates a better performance. 
One can observe that this performance varies widely across models and topics. 
While computational chemistry and biochemistry receive relatively high scores for many models, this is not the cases for topics such as chemical safety or analytical chemistry.
In the subfield of analytical chemistry the prediction of the number of peaks observable in a \gls{nmr} spectrum proved difficult for the models (e.g., \SI{\variable{outputs/subset_scores/is_number_nmr_peaks_gpt-4.txt}}{\percent}). 
While this question is relatively easy (\SI{\variable{outputs/human_subset_scores/is_number_nmr_peaks.txt}}{\percent}) for trained humans given a drawing of the compounds, models that are only shown the \gls{smiles} string of a compound have to use this to reason about the symmetry of the compound. 
This is mirrored in the questions about point groups of compounds, which is models struggle with more than humans ().

@@

\section*{Data and code availability}
The code and data for chembench is available at \url{https://github.com/lamalab-org/chem-bench} and archived at \url{XXX}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}. 
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{showyourwork!} framework.\cite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{https://github.com/lamalab-org/chembench-paper}. 
To facilitate reproduction, some intermediate results of the analysis are cached at \url{http://dx.doi.org/10.5072/zenodo.34706}.
